Scalar on Function Regression

### 2022-01-02 Presentation/slides.tex
PCA & Karhunen-Loeve Stuff

	\begin{frame}{Principal Component Analysis}
		Setting: $Y = X\beta + \epsilon$ \: with standardized regressors in $X$ \\
		Goal: \textbf{Dimension Reduction} 
		\vspace{0.3cm}

		Let $\Sigma_X = Cov(x)$ and let $\{\lambda_i\}_{i \in \mathcal{I}}$ be the \textbf{Eigenvalues} of $\Sigma_X$ and $\{\gamma_i\}_{i \in \mathcal{I}}$ be the \textbf{Eigenvectors} of $\Sigma_X$.
	\end{frame}

@@

		Where the $\xi_j$ are scalar-valued random variables with variance $\lambda_j$.\\
		This representation is called the \textbf{Karhunen-Lo\'{e}ve Expansion} of the random function $F$ and the Eigenfunctions can serve as a basis to represent the function.
	\end{frame}

>>>>

	\begin{frame}{Spectral Representation of Random Vectors}
		Let $X(\omega)$ be a random vector realizing in $\mathbb{R}^p$.

		\begin{itemize}
			\item Let $\mu_x = \mathbb{E}(X)$ and $\Sigma_X = Cov(X)$
			\item Let $\{\gamma_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\Sigma_X$
			\item Let $\{\lambda_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\Sigma_X$
		\end{itemize}

		\vspace{0.2cm}
		Then $X$ can also be represented as
		$$X(\omega) = \mu_x + \sum_{i = 1}^{p} \xi_i(\omega) \gamma_i$$
		where the $\xi_i(\omega)$ have the following properties

		\begin{multicols}{2}
			\begin{enumerate}
				\item $\mathbb{E}[\xi_i(\omega)] = 0$
				\item $var(\xi_i(\omega)) = \lambda_i$
				\item $Cov(\xi_i(\omega), \xi_j(\omega)) = 0$ for $i \neq j$
			\end{enumerate}
		\end{multicols}
	\end{frame}

	\begin{frame}{Principal Component Analysis}
		$\Sigma_X$ unknown $\rightarrow$ \textbf{sample analogues}

		\begin{itemize}
			\item Let $\mathbf{X} \in \mathbb{R}^{n \times p}$ be the matrix containing the standardized regressors in the usual configuration.
			\item Let $\hat{\Sigma}_X = \frac{\mathbf{X}'\mathbf{X}}{n}$
			\item Let $\{\hat{\gamma}_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\hat{\Sigma}_X$
			\item Let $\{\hat{\lambda}_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\hat{\Sigma}_X$
		\end{itemize}

	\end{frame}

@@

		Where the $\xi_j$ are scalar-valued random variables with the following properties.
		\begin{multicols}{2}
			\begin{enumerate}
				\item $\mathbb{E}[\xi_i(\omega)] = 0$
				\item $var(\xi_i(\omega)) = \lambda_i$
				\item $Cov(\xi_i(\omega), \xi_j(\omega)) = 0$ for $i \neq j$
			\end{enumerate}
		\end{multicols}

		This representation is called the \textbf{Karhunen-Lo\'{e}ve Expansion} of the random function $F$ and the Eigenfunctions can serve as a basis to represent the function.
	\end{frame}
